Pre-/Post-Trikafta in CFRD

### 2022-02-02 Christine Chan/Pre-post Trikafta/pre_post_trikafta_merge.Rmd
Update pre_post_trikafta_merge.Rmd

###### IMPORT UM DATA ########
um_all <- read_csv("./Prepost Triakfta/Data_Cleaned/um_all.csv")
###################################

@@

####### UM  ############
# to do: rename variables to match CHCO
# most variables have mult columns and no notation: FEV, A1C, FVC, CFRD Status, etc
um_all %>% select(`CFF ID`, `CFRD Status...10`, `CFRD Status...34`) %>% filter(`CFRD Status...10` != `CFRD Status...34`)

>>>>

###### IMPORT UM DATA ########
#um_all <- read_csv("./Prepost Triakfta/Data_Cleaned/um_all.csv")
###################################

@@

####### UM  ############
# to do: rename variables to match CHCO
# most variables have mult columns and no notation: FEV, A1C, FVC, CFRD Status, etc
#um_all %>% select(`CFF ID`, `CFRD Status...10`, `CFRD Status...34`) %>% filter(`CFRD Status...10` != `CFRD Status...34`)
